---
title: "datasetxxx"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r wrap_lines}
library(knitr) 
opts_chunk$set(tidy.opts=list(width.cutoff=25),tidy=TRUE)
```

```{r H1Bvisa_map}
library(tidyverse)
library(maps)
hire<-read_csv("/Users/yzh/Downloads/h1b_kaggle.csv")
hire[1:10,]
hire2016certi<- filter(hire, CASE_STATUS=="CERTIFIED",YEAR==2016,PREVAILING_WAGE<=250000,40000<=PREVAILING_WAGE)
us<-map_data("usa")
ggplot(us)+geom_polygon(aes(x=long, y=lat,group=group), fill=NA,color="red")+geom_point(data=hire2016certi,aes(x=lon,y=lat,size=PREVAILING_WAGE),color="blue",alpha=0.002,position="jitter")+coord_map()+xlim(c(-126,-62.5))+
ylim(c(24,50))
```


-------------------------------
-------------------------------------------------
Prob 3

Create a bar plot showing the total number of enrolled students of each race.
missing values are represented in CSV file as: -2, -5 -9

Data from:
SCH_ENR_HI_M,62,1,Overall Student Enrollment: Hispanic Male,I,7
SCH_ENR_HI_F,63,1,Overall Student Enrollment: Hispanic Female,I,7
SCH_ENR_AM_M,64,1,Overall Student Enrollment: American Indian/Alaska Native Male,I,7
SCH_ENR_AM_F,65,1,Overall Student Enrollment: American Indian/Alaska Native Female,I,7
SCH_ENR_AS_M,66,1,Overall Student Enrollment: Asian Male,I,7
SCH_ENR_AS_F,67,1,Overall Student Enrollment: Asian Female,I,7
SCH_ENR_HP_M,68,1,Overall Student Enrollment: Native Hawaiian/Pacific Islander Male,I,7
SCH_ENR_HP_F,69,1,Overall Student Enrollment: Native Hawaiian/Pacific Islander Female,I,7
SCH_ENR_BL_M,70,1,Overall Student Enrollment: Black Male,I,7
SCH_ENR_BL_F,71,1,Overall Student Enrollment: Black Female,I,7
SCH_ENR_WH_M,72,1,Overall Student Enrollment: White Male,I,7
SCH_ENR_WH_F,73,1,Overall Student Enrollment: White Female,I,7
SCH_ENR_TR_M,74,1,Overall Student Enrollment: Two or More Races Male,I,7
SCH_ENR_TR_F,75,1,Overall Student Enrollment: Two or More Races Female,I,7

```{r prob3}
library(tidyverse)
crdc<-read_csv("CRDC2013_14_SCH.csv",na=c("-2","-5","-9"))
race<-transmute(crdc, hispanic=SCH_ENR_HI_M+SCH_ENR_HI_F, 
                Indian_or_Alaska=SCH_ENR_AM_M+SCH_ENR_AM_F, Asian = SCH_ENR_AS_M + SCH_ENR_AS_F, 
                Hawaiian_ot_Pacific = SCH_ENR_HP_M + SCH_ENR_HP_F, Black = SCH_ENR_BL_M + SCH_ENR_BL_F, 
                White=SCH_ENR_WH_M+SCH_ENR_WH_F, Two_or_More_Races = SCH_ENR_TR_M + SCH_ENR_TR_F)
stats<-summarize(race, sum(hispanic, na.rm=T), sum(Indian_or_Alaska, na.rm=T), sum(Asian, na.rm=T),
                 sum(Hawaiian_ot_Pacific, na.rm=T ), sum(Black, na.rm=T), sum(White, na.rm=T), sum(Two_or_More_Races, na.rm=T))
plotdata<- data.frame(races=c("hispanic","Indian_or_Alaska", "Asian", "Hawaiian_ot_Pacific", "Black", "White", "Two_or_More_Races" ), population=c(stats[[1]],stats[[2]],stats[[3]],stats[[4]],stats[[5]], stats[[6]],stats[[7]]))

ggplot(data=plotdata)+geom_col(aes(x=races, y=population))+theme(axis.text.x = element_text(angle=45, hjust=1) )

```

---------------------------
---------------------------------------------
Prob 4
Create a bar plot showing the number of students of each race enrolled in a Calculus class. Comment on any similarities or differences between this distribution and the one you plotted in Problem 3.

Data from:
SCH_MATHENR_CALC_HI_M,426,1,Students Enrolled in Calculus: Hispanic Male,I,19
SCH_MATHENR_CALC_HI_F,427,1,Students Enrolled in Calculus: Hispanic Female,I,19
SCH_MATHENR_CALC_AM_M,428,1,Students Enrolled in Calculus: American Indian/Alaska Native Male,I,19
SCH_MATHENR_CALC_AM_F,429,1,Students Enrolled in Calculus: American Indian/Alaska Native Female,I,19
SCH_MATHENR_CALC_AS_M,430,1,Students Enrolled in Calculus: Asian Male,I,19
SCH_MATHENR_CALC_AS_F,431,1,Students Enrolled in Calculus: Asian Female,I,19
SCH_MATHENR_CALC_HP_M,432,1,Students Enrolled in Calculus: Native Hawaiian/Pacific Islander Male,I,19
SCH_MATHENR_CALC_HP_F,433,1,Students Enrolled in Calculus: Native Hawaiian/Pacific Islander Female,I,19
SCH_MATHENR_CALC_BL_M,434,1,Students Enrolled in Calculus: Black Male,I,19
SCH_MATHENR_CALC_BL_F,435,1,Students Enrolled in Calculus: Black Female,I,19
SCH_MATHENR_CALC_WH_M,436,1,Students Enrolled in Calculus: White Male,I,19
SCH_MATHENR_CALC_WH_F,437,1,Students Enrolled in Calculus: White Female,I,19
SCH_MATHENR_CALC_TR_M,438,1,Students Enrolled in Calculus: Two or More Races Male,I,19
SCH_MATHENR_CALC_TR_F,439,1,Students Enrolled in Calculus: Two or More Races Female,I,19

```{r prob4}
race_cal<-transmute(crdc, hispanic=SCH_MATHENR_CALC_HI_M+SCH_MATHENR_CALC_HI_F, 
                Indian_or_Alaska=SCH_MATHENR_CALC_AM_M+SCH_MATHENR_CALC_AM_F, Asian = SCH_MATHENR_CALC_AS_M + SCH_MATHENR_CALC_AS_F, 
                Hawaiian_ot_Pacific = SCH_MATHENR_CALC_HP_M + SCH_MATHENR_CALC_HP_F, Black = SCH_MATHENR_CALC_BL_M + SCH_MATHENR_CALC_BL_F, 
                White=SCH_MATHENR_CALC_WH_M+SCH_MATHENR_CALC_WH_F, Two_or_More_Races = SCH_MATHENR_CALC_TR_M + SCH_MATHENR_CALC_TR_F)
stats_cal<-summarize(race_cal, sum(hispanic, na.rm=T), sum(Indian_or_Alaska, na.rm=T), sum(Asian, na.rm=T),
                 sum(Hawaiian_ot_Pacific, na.rm=T ), sum(Black, na.rm=T), sum(White, na.rm=T), sum(Two_or_More_Races, na.rm=T))
plotdata_cal<- data.frame(races=c("hispanic","Indian_or_Alaska", "Asian", "Hawaiian_ot_Pacific", "Black", "White", "Two_or_More_Races" ), population=c(stats_cal[[1]],stats_cal[[2]],stats_cal[[3]],stats_cal[[4]],stats_cal[[5]], stats_cal[[6]],stats_cal[[7]]))

ggplot(data=plotdata_cal)+geom_col(aes(x=races, y=population))+theme(axis.text.x = element_text(angle=45, hjust=1) )
```
Asian are over-represented in calculus classes.Black and hispanic are under-represented.

---------------------------------------
-----------------------------------
Prob 5
```{r prob5}
library(DBI) 
library(RMySQL) 
library(dbplyr)
con <- dbConnect(MySQL(), dbname = "dblp",username="root",password="mysql")
author<-tbl(con, "authors")
general<-tbl(con, "general")
author %>% filter(prob>0.95,prob<=1) %>% group_by(name) %>% mutate(G=ifelse(gender=="M",1,0)) %>% summarize(Gx=sum(G)) %>% transmute(g=ifelse(Gx>0,"M","F")) %>% group_by(g) %>% summarize(number=n()) %>% collect() %>% ggplot()+geom_col(aes(x=g,y=number))
```


------------------------------
------------------------------

Prob6
Again including only the authors for whom a gender was predicted with a probability of 0.95 or greater, create a stacked bar plot showing the number of distinct male and female authors published each year.

```{r prob6}
authorinfo<-left_join(author, general, by="k")
pd<-authorinfo %>% filter(prob>0.95,prob<=1) %>% mutate(G=ifelse(gender=="M",1,0)) %>% group_by(name,year) %>% summarize(Gx=sum(G)) %>% mutate(g=ifelse(Gx>0,"M","F"))

ggplot(collect(pd)) + geom_bar(aes(x=year,fill=g),position="stack")+theme(axis.text.x = element_text(angle=45, hjust=1))
                                                                                                                                                                                                        
```

-----------------------------------
----------------------------------------

Prob 7
```{r prob7}
ggplot(collect(pd)) + geom_bar(aes(x=year,y=..count../sum(..count..),fill=g),position="stack")+theme(axis.text.x = element_text(angle=45, hjust=1))
```

-----------------------------------
----------------------------------------

Prob 8
```{r prob8}
load("/Users/yzh/Desktop/R data/HW2 data/ICPSR_31721/DS0001/31721-0001-Data.rda")
nofactor <- data.frame(lapply(da31721.0001, as.character), stringsAsFactors=FALSE)
health<-filter(nofactor,is.na(Q6)==F, is.na(Q96)==F,is.na(Q106)==F)
nonbi <- mutate(health,  
                Non_binary= ifelse(Q6=="(4) Androgynous" | Q6=="(6) Gender Queer",Q6, "not Non-Binary"),
                Transwoman_info=ifelse(Q5=="(1) Male" & Q6=="(3) Transgender", "Transwoman", "Not Transwoman"),
                Transman_info=ifelse(Q5=="(2) Female" & Q6=="(3) Transgender", "Transman", "Not Transman"), assault=ifelse(Q96 == "(1) Yes" | Q106 == "(1) No", T,F))
ggplot(nonbi)+geom_bar(aes(x=Non_binary, y=..count../sum(count), fill= assault),position="stack")
ggplot(nonbi)+geom_bar(aes(x=Transwoman_info, y=..count../sum(count), fill= assault),position="stack")
ggplot(nonbi)+geom_bar(aes(x=Transman_info, y=..count../sum(count), fill= assault),position="stack")




```
Note: I plotted 2 barplots since in problem "barplots" indicates multiple plots
-----------------------------------
----------------------------------------

Prob9
Q131: Have you ever thought about killing yourself?
```{r prob9}
sui<-filter(nofactor,is.na(RACE)==F, is.na(Q131)==F)
racesui <- mutate(sui,  
                black= ifelse(RACE=="(1) African American (Black)",RACE, "not Black"),
                white= ifelse(RACE=="(2) White (Caucasian)",RACE, "not white"),
                Hispanic_Latinx = ifelse(RACE=="(3) Hispanic or Latino/Latina",RACE, "not hispanic"),
                Native_American = ifelse(RACE=="(4) Native American/American Indian",RACE, "not native american")
                )
library(plyr)
racesui<-rename(racesui,c("Q131"="whether_attempted_suicide"))
library(dplyr)
ggplot(racesui)+geom_bar(aes(x=black, y=..count../sum(count), fill= whether_attempted_suicide),position="stack")
ggplot(racesui)+geom_bar(aes(x=white, y=..count../sum(count), fill= whether_attempted_suicide),position="stack")
ggplot(racesui)+geom_bar(aes(x=Hispanic_Latinx, y=..count../sum(count), fill= whether_attempted_suicide),position="stack")
ggplot(racesui)+geom_bar(aes(x=Native_American, y=..count../sum(count), fill= whether_attempted_suicide),position="stack")

suitotal<-filter(nofactor,is.na(Q131)==F)
totalsui <- transmute(suitotal,suicide= ifelse(Q131=="(1) Yes",T, F))
summarize(totalsui,proportion=mean(suicide,na.rm=T))                    
```
It is higher than the national average.

Note: I plotted 4 barplots since in problem "barplots" indicates multiple plots
-----------------------------------
----------------------------------------

Prob10

```{r prob10}
suifam<-filter(nofactor,is.na(Q119)==F, is.na(Q131)==F)
suifam2<-filter(suifam,Q119!="(5) Not applicable to me")
library(plyr)
suifam2<-rename(suifam2,c("Q131"="whether_attempted_suicide"))
library(dplyr)
ggplot(suifam2)+geom_bar(aes(x=Q119, y=..count../sum(count), fill= whether_attempted_suicide),position="stack")+
  theme(axis.text.x = element_text(angle=45, hjust=1) )
```
Note: Although in problem "barplots" indicates multiple plots , I feel one barplot is enough and clear
